Aneuploidy can be an evolutionary detour \\ on the path to adaptation

### 2022-10-13 ms/ms.tex
update authors, acks, affil

\author[1,2,*]{Ilia Kohanovski}
\author[1,*]{Martin Pontz}
\author[3]{Avihu H. Yona}
\author[1,$\dagger$]{Yoav Ram}

\affil[1]{School of Zoology, Faculty of Life Sciences, Tel Aviv University, Tel Aviv, Israel}
\affil[2]{School of Computer Science, Reichman University, Herzliya, Israel}
\affil[3]{Institute of Biochemistry, Food Science and Nutrition,
Robert H. Smith Faculty of Agriculture, Food and Environment,
The Hebrew University of Jerusalem, Israel}
\affil[*]{These authors contributed equally to this work}
\affil[$\dagger$]{Corresponding author: yoav@yoavram.com}

@@

% Acknowledgements
{\small
\section*{Acknowledgements}
We thank Yitzhak Pilpel, Orna Dahan, Lilach Hadany, Judith Berman, David Gresham, Shay Covo, Martin Kupiec, Uri Obolski, Daniel Weissman, and Tal Simon for discussions and comments.
This work was supported in part by 
the Israel Science Foundation~(ISF, YR 552/19),
the US--Israel Binational Science Foundation~(BSF, YR 2021276)
Minerva Stiftung center for Lab Evolution~(YR),
Minerva Stiftung short-term research grant~(MP).
}

>>>>

\author[a,b,*]{Ilia Kohanovski}
\author[a,*]{Martin Pontz}
\author[c]{Orna Dahan}
\author[c]{Yitzhak Pilpel}
\author[d]{Avihu H. Yona}
\author[a,1]{Yoav Ram}

\affil[a]{School of Zoology, Faculty of Life Sciences, Tel Aviv University, Tel Aviv, Israel}
\affil[b]{School of Computer Science, Reichman University, Herzliya, Israel}
\affil[c]{Department of Molecular Genetics, Weizmann Institute of Science, Rehovot 76100, Israel}
\affil[d]{Institute of Biochemistry, Food Science and Nutrition,
Robert H. Smith Faculty of Agriculture, Food and Environment,
The Hebrew University of Jerusalem, Israel}
\affil[*]{These authors contributed equally to this work}
\affil[1]{Corresponding author: yoav@yoavram.com}

@@

% Acknowledgements
{\small
\section*{Acknowledgements}
We thank Lilach Hadany, Judith Berman, David Gresham, Shay Covo, Martin Kupiec, Uri Obolski, Daniel Weissman, and Tal Simon for discussions and comments.
This work was supported in part by 
the Israel Science Foundation~(ISF, YR 552/19),
the US--Israel Binational Science Foundation~(BSF, YR 2021276)
Minerva Stiftung center for Lab Evolution~(YR),
Minerva Stiftung short-term research grant~(MP).
}
